Dynamically Annealed Reinforcement Learning for Intrusion Prevention

### 2017-11-09 paper/paper.tex
[Paper] A to-do list for consideration

\title{Dynamically Annealed Reinforcement Learning for Intrusion Prevention}
\author{Kyle A. Simpson\thanks{This work was supported by the Engineering and Physical Sciences
		Research Council [grant number EP/M508056/1]},\\\emph{University of Glasgow, Glasgow, Scotland},\\
		\email{k.simpson.1@research.gla.ac.uk}}
\date{}

@@

Testing to see if I get the right header behaviour.

>>>>

\title{Dynamically Annealed Reinforcement Learning for Intrusion Prevention}
\author{Kyle A. Simpson\thanks{This work was supported by the Engineering and Physical Sciences
		Research Council [grant number EP/M508056/1]},\\\emph{University of Glasgow, Glasgow, Scotland},\\
		\email{k.simpson.1@research.gla.ac.uk}}

% Remove date, leave no spacing.
\predate{}
\postdate{}
\date{}

@@

Testing to see if I get the right header behaviour.
Another sentence to bring out the edge cases in this style.

Does next paragraph have proper indent? Please!

\section{A Plan, of Sorts}

\begin{enumerate}
	\item Establish criteria used to inform system temp---what could make my system increase $\epsilon$ again late into training?
	\item What are my chosen features? Reward Function?
	\item Test against MARL and others---probably essential.
	\item Model at least three scenarios: standard (under attack), normality shifts, attack changes.
	\item \textsc{Ideally:} test adversarial work (what do such examples look like for my classifier, can an attacker actually operate on them?). How do results change with/without pretraining?
\end{enumerate}
